---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

library(tidyverse)
```

```{css}
body {
  font-family: Arial, sans-serif;
  line-height: 1.7;
  color: #222222;
  max-width: 900px;
  margin: auto;
  padding: 20px;
}

h2 {
  color: #2c3e50;
  border-bottom: 2px solid #d9e2ec;
  padding-bottom: 8px;
}

p {
  font-size: 16px;
  margin-bottom: 14px;
}

figure {
  display: block;
  margin: 24px 0;
  width: 100%;
}

img {
  display: block;
  max-width: 100%;
  height: auto;
  margin: 0 auto;
}

pre {
  display: block;
  max-width: 100%;
  overflow-x: auto;
}

strong {
  color: #1f4e79;
}
```

## What can be learned from my vehicle observations?

This dynamic report presents observational data about vehicles I recorded over time. The data focuses on four main features: the type of vehicle observed, the brand origin, the cleanliness score, and whether the vehicle appeared new or not.

The purpose of this report is to summarise key patterns in the observations and demonstrate how a dynamic report can automatically update when new responses are added to the linked Google Form and Google Sheet.

```{r fig.width=8, fig.height=4}
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vSFTm-eXrXyj3gEA9BOLHDY30t5utk1GmSt5hfCN8Hj_2RIbzgxa89WVtzMqK3DCbDLXA0a8XdnZfq0/pub?gid=1704931853&single=true&output=csv")

latest_data <- logged_data %>%
  rename(
    vehicle_type = 2,
    brand_origin = 3,
    cleanliness = 4,
    is_new = 5
  )

report_num_obs <- nrow(latest_data)

report_mean_clean <- latest_data$cleanliness %>%
  mean(na.rm = TRUE) %>%
  round(1)

report_max_clean <- latest_data$cleanliness %>%
  max(na.rm = TRUE)

most_common_vehicle <- latest_data %>%
  count(vehicle_type, sort = TRUE) %>%
  slice(1) %>%
  pull(vehicle_type)

most_common_origin <- latest_data %>%
  count(brand_origin, sort = TRUE) %>%
  slice(1) %>%
  pull(brand_origin)
```
A total of `r report_num_obs` vehicle observations were recorded in this dataset.

The average cleanliness score was `r report_mean_clean`, while the highest cleanliness score recorded was `r report_max_clean`.

The most commonly observed vehicle type was `r most_common_vehicle`, and the most common brand origin was `r most_common_origin`.
```{r fig.width=8, fig.height=4}
latest_data %>%
  ggplot(aes(x = vehicle_type)) +
  geom_bar() +
  theme_minimal() +
  labs(
    title = "Vehicle Type Distribution",
    x = "Vehicle type",
    y = "Count"
  )
```
The bar chart above shows the distribution of vehicle types in the dataset. This makes it easier to identify which kinds of vehicles appeared most often during the observation period.
```{r}
latest_data %>%
  ggplot(aes(x = brand_origin)) +
  geom_bar() +
  theme_minimal() +
  labs(
    title = "Brand Origin Distribution",
    x = "Brand origin",
    y = "Count"
  )
```
This second bar chart compares the brand origins of the vehicles observed. It provides a simple way to see which brand origins appeared more frequently in the dataset.

Overall, this report shows how observational data can be collected, summarised, and communicated visually through R Markdown. Because the report is connected to a published CSV, the summaries and graphs can change automatically when more observations are added.
